---
title: "CNV Report"
date: "`r format(Sys.time(), \"%Y-%m-%d %H:%M %Z\")`"
output:
  html_document:
    theme: cosmo
    highlight: tango
    code_folding: hide
    toc: false
params:
  cnv_gene: ""
  cnv_segment: ""
---

```{r setup, include=FALSE}
library(readr)
library(DT)
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```


This report provides an interactive view of Copy Number Variation (CNV) results at both the gene and segment level. 

---

<details>
<summary><strong>Input data (click to expand)</strong></summary>

- **Gene-level CNV file:** `r params$cnv_gene`
- **Segment-level CNV file:** `r params$cnv_segment`

</details>


<details>
<summary><strong>How to use the tables (click to expand)</strong></summary>

The tables below allow sorting and filtering.

**Sorting** - Click any column header to sort ascending or descending.

**Filtering** - Use the boxes at the top of each column to filter results. The tables support **regular expression (regex)** search:

  - Exact match (recommended for genes): `^TP53$` → matches only TP53
  - Starts with: `^BRCA`
  - Ends with: `TP53$`

</details>

---


```{r load-data}
cnv_gene <- read_tsv(params$cnv_gene)
cnv_segment <- read_tsv(params$cnv_segment)
```

## Gene-level CNV results

This table summarizes CNV calls at the gene level.

```{r gene-table}
datatable(
  cnv_gene,
  filter = "top",
  options = list(
    pageLength = 10,
    autoWidth = TRUE,
    search = list(regex = TRUE)
  ),
  rownames = FALSE
) 
```


## Segment-level CNV results

This table summarizes CNV calls at the genomic segment level.

```{r segment-table}
datatable(
  cnv_segment,
  filter = "top",
  options = list(
    pageLength = 10,
    autoWidth = TRUE,
    search = list(regex = TRUE)
  ),
  rownames = FALSE
)
```
